OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-06-05 main.tex
fixing small typos

Unlike the other methods, OneD corrects a single variable instead of the
whole matrix. It uses only the total number of contacts per bin and thus
estimates the model parameters much faster than previous explicit methods.
We measured the running time of the different tools on a 3.3~GHz machine
with 62 GB~RAM, always using the default parameters. Figure~\ref{fig:times}A
shows the running times of the different methods on the samples described
in Table~\ref{tab:samples} at 100 kbp resolution. The fastest method is
\textit{vanilla} and the slowest is \textit{lgf}, with an over 100-fold
span between the two. OneD also scales well in terms of bin size, as can
be seen in Figure~\ref{fig:times}B, where the different corrections were
applied to a reduced part of the genome at increasing resolutions.

>>>>

Unlike the other methods, OneD corrects a single variable instead of the
whole matrix. It uses only the total number of contacts per bin and thus
estimates the model parameters much faster than previous explicit methods.
We measured the running time of the different tools on a 3.3~GHz machine
with 62 GB~RAM, always using the default parameters. Figure~\ref{fig:times}A
shows the running times of the different methods on the samples described
in Table~\ref{tab:samples} at 100 kbp resolution. The fastest method is
\textit{vanilla} and the slowest is \textit{lgf}, with an over 100-fold
span between the two. OneD also scales well in terms of bin size, as it can
be seen in Figure~\ref{fig:times}B, where the different corrections were
applied to a reduced part of the genome at increasing resolutions.
